MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-28 paper.Rmd
Working on package URLs

<!-- Define some macros to use later -->
[link-cran]:             https://cran.r-project.org
[link-ieatools]:         https://github.com/MatthewHeun/IEATools
[link-ieaweeb]:          https://www.iea.org/data-and-statistics/data-product/world-energy-balances
[link-ilo]:              https://www.ilo.org/
[link-fao]:              https://www.fao.org/
[link-matsbyname]:       https://github.com/MatthewHeun/matsbyname
[link-matsindf]:         https://github.com/MatthewHeun/matsindf
[link-mwtools]:          https://github.com/EnergyEconomyDecoupling/MWTools
[link-pfusetup]:         https://github.com/energyeconomydecoupling/PFUSetup
[link-pfudatabase]:      https://github.com/energyeconomydecoupling/PFUDatabase
[link-pfuaggdatabase]:   https://github.com/EnergyEconomyDecoupling/PFUAggDatabase
[link-pfupipelinetools]: https://github.com/EnergyEconomyDecoupling/PFUPipelineTools
[link-rclabels]:         https://github.com/MatthewHeun/RCLabels
[link-recca]:            https://github.com/MatthewHeun/Recca
[link-targets]:          https://docs.ropensci.org/targets
[link-tidyverse]:        https://www.tidyverse.org

>>>>

<!-- Define some macros to use later -->
[link-cran]:             https://cran.r-project.org
[link-ieatools]:         https://github.com/MatthewHeun/IEATools
[link-ieaweeb]:          https://www.iea.org/data-and-statistics/data-product/world-energy-balances
[link-ilo]:              https://www.ilo.org/
[link-fao]:              https://www.fao.org/
[link-matsbyname]:       https://github.com/MatthewHeun/matsbyname
[link-matsindf]:         https://github.com/MatthewHeun/matsindf
[link-mwtools]:          https://github.com/EnergyEconomyDecoupling/MWTools
[link-pfusetup]:         https://github.com/EnergyEconomyDecoupling/PFUSetup
[link-pfudatabase]:      https://github.com/EnergyEconomyDecoupling/PFUDatabase
[link-pfuaggdatabase]:   https://github.com/EnergyEconomyDecoupling/PFUAggDatabase
[link-pfupipelinetools]: https://github.com/EnergyEconomyDecoupling/PFUPipelineTools
[link-rclabels]:         https://github.com/MatthewHeun/RCLabels
[link-recca]:            https://github.com/MatthewHeun/Recca
[link-targets]:          https://docs.ropensci.org/targets
[link-tidyverse]:        https://www.tidyverse.org
